\subsubsection{Matching Pairs Reduction}

Before we lift the assumption $\alpha_M = 2$, we present why it was necessary in the previous reduction.
Let $(x,y)$ be the constructed \lcs{} instance as before.
Per definition of matching pairs, we know $M(x,y) \geq \numSymbols{0}{x} \cdot \numSymbols{0}{y}$.
Looking at the construction, we have $\bigO{A}$ blocks of $O^\gamma$ in $x$.
From \autoref{thm:small_lcs_construction} and \autoref{thm:nvg} we further know $\gamma \geq |\nvg{a_i}| = \Theta(D)$. 
Hence, $\numSymbols{0}{x} \geq \bigO{AD}$.
In $y$ we have one block $0^{A\gamma'}$ at the beginning of $y$, so $\numSymbols{0}{y} \geq |0^{A\gamma'}| = A\gamma' \geq \bigO{AD}$ where we bounded $\gamma'$ similar to $\gamma$.
In total we have $M(x,y) \geq \bigO{(AD)^2} = \bigO{n(x,y)^2}$ and therefore $\alpha_M \geq 2$.
However, there is a parameter setting with $\alpha_M < 2$, e.g., for $\Sigma = \{ \sigma_1, \ldots, \sigma_n \}$ we can define $x = y := \sigma_1 \cdots \sigma_n$.
In this case, we have $\alpha_m = \alpha_L = \alpha_\Sigma = \alpha_d = 1$, $\alpha_\delta = \alpha_\Delta = 0$ and $\alpha_M = 1 < 2$.


To reduce our matching pairs, we can look at the parameter relation from \autoref{sec:fin_param_rels} specifically \autoref{thm:matching_pairs_lb}.
Here we have shown that $M \geq \frac{L^2}{|\Sigma|}$.
Hence, we have the chance to reduce $M$ by increasing the alphabet size.
The authors used therefore the following lemma.

\begin{lemma}[Crossing Alphabets]
\footnote{Copied from \cite[Lemma 9.3]{Bringman.2018}. The proof can be seen there.}
Let $\Sigma_1,\ldots,\Sigma_k$ be disjoint alphabets and let $x_i,y_i$ be strings
over alphabet $\Sigma_i$. Consider $x := x_1 \cdots x_k$ and $y := y_k \cdots y_1$,
i.e., the order in $y$ is reversed. For any parameter $p \in \{n,m,|\Sigma|,M,d\}$
we have
\(
  p(x,y) \;=\; \sum_{i=1}^k p(x_i,y_i).
\)
Moreover,
\(
  L(x,y) \;=\; \max_i L(x_i,y_i).
\)
\end{lemma}


Todo:

Show construction and give an intuition for the proof (not full proof).